Privacy-Preserving Localisation Using Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-10-15 main.tex
Updated notations to denote filter estimates as x_{k|k} allowing the identification of prediction and update steps in the filter - also added it in notation paragraph - still need to do whole read-through but looks like it was done properly from first look

\subsection{Notation}
Throughout this work, we will use the following notation. Lowercase characters are scalars, $a$, vectors are underlined, $\vec{a}$, and random variables are bold, $\rv{a}$. Uppercase bold characters are matrices, $\mat{A}$, with $\mat{A}^{-1}$ denoting the inverse and $\mat{A}^\top$ the transpose. $|a|$ is the absolute value of $a$ and $\lVert\vec{a}\rVert$ the vector normal. $\E{\cdot}$ and $\Var{\cdot}$ are used for the expected value and variance, respectively, and encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$. Additionally, key $k$ may be ommited when inferrable from context. $\lfloor\cdot\rceil$ rounds to the nearest integer, $a\|b$ stands for a bitwise concatenation of $a$ and $b$ and sets will be written as $\{\dots\}$ while ordered sequences as $\langle\dots\rangle$.

@@

The navigator state is defined as 
\begin{equation}
    \rvec{x} = 
    \begin{bmatrix}
        \rv{x} & \rv{dx} & \rv{y} & \rv{dy}
    \end{bmatrix}^\top\,. \label{eqn:state_def}
\end{equation}
A known process model is followed, which at time $k$ is given by
\begin{equation}
    \rvec{x}_k = \vec{f}(\rvec{x}_{k-1})+\rvec{w}_k\,, \label{eqn:process_model}
\end{equation}
with zero-mean Gaussian process noise $\rvec{w}_k \sim \mathcal{N}(\vec{0},\mat{Q})$. The measurement model is dependant on sensor $i$ and given by
\begin{equation}
    \rv{z}_{k,i} = h_i(\rvec{x}_k)+\rv{v}_{k,i}\,, \label{eqn:measurement_model}
\end{equation}
with noise $\rv{v}_{k,i} \sim \mathcal{N}(0,r_i)$, with measurement function $h_i$, for sensor $i$ at location
\begin{equation}
    \vec{s}_i = 
    \begin{bmatrix}
        s_{x,i} & s_{y,i}
    \end{bmatrix}^\top\,,
\end{equation} 
is defined as
\begin{equation}
    \begin{split}
        h_i(\rvec{x}_k) &= \left\lVert
        \begin{bmatrix}
            \rv{x}_k & \rv{y}_k
        \end{bmatrix}^\top
        - \vec{s}_{i}\right\rVert \\
        &= \sqrt{(\rv{x}_k-s_{x,i})^2 + (\rv{y}_k-s_{y,i})^2}\,.
    \end{split}
\end{equation}
We wish to run a state estimation filter with models \eqref{eqn:process_model} and \eqref{eqn:measurement_model} such that all involved sensors $1 \leq i \leq n$ do not learn the estimated state $\rvec{x}_k$ and the navigator does not learn sensor locations $\vec{s}_i,\,1 \leq i \leq n$, measurement variances $r_i$ or their measurements $\rv{z}_{k,i}$ at any time $k$. We motivate these goals with the example of aircraft navigation in the presence of privately-operated range-measuring stations. It is reasonable to assume that the current state of an aircraft may not wish to be disclosed to unknown parties and, similarly, that tower locations may wish to be kept private from unidentified navigating aircraft. However, the additional safety to passengers provided by accurate aircraft localisation, may be a goal of all those involved justifying their cooperation.

@@

\begin{pf}
    Consider adversary $\mathcal{A}$ playing the LCAO game defined in Section \ref{subsec:lcao}. The following is a construction of an adversary $\mathcal{A}'$ playing the AO game in Appendix \ref{app:ao} against a challenger $\mathcal{C}$ using the Joye-Libert aggregation scheme from Section \ref{subsec:joye_libert_scheme}.
    \begin{description}
        \item[Setup] When receiving $N$ and $H$ as public parameters from $\mathcal{C}$, choose an $m>1$ and give public parameter $H$, number of weights $m$, and $pk_0=N$ to $\mathcal{A}$.
        \item[Queries] Handle queries from $\mathcal{A}$:
        \begin{description}
            \item[\textit{Weight Query}] When $\mathcal{A}$ submits a weight query $t$, choose weights $\omega^{(t)}_j,\,1 \leq j \leq m$ and random values $r_j \in \mathbb{Z}_N,\,1 \leq j \leq m$, and return encryptions 
            \begin{equation*}
                (N+1)^{\omega^{(t)}_{j}}r_j^N\pmod{N^2},\,1\leq j\leq m
            \end{equation*}
            to $\mathcal{A}$.
            \item[\textit{Combine Query}] When $\mathcal{A}$ submits combine query $(i, t, x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$, choose weights $\omega^{(t)}_j,1 \leq j \leq m$ if not already chosen for the instance $t$, and make an AO encryption query $(i, t, \sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ to $\mathcal{C}$. The received response is of the form $(N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}H(t)^{sk_i}$; multiply it by $r^N$ for a random $r \in \mathbb{Z}_N$ and return 
            \begin{equation*}
                (N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r^N H(t)^{sk_i} \pmod{N^2}
            \end{equation*}
            to $\mathcal{A}$.
            \item[\textit{Compromise Query}] When $\mathcal{A}$ submits compromise query $i$, make the same compromise query $i$ to $\mathcal{C}$, and return the recieved secret key $sk_i$ to $\mathcal{A}$.
        \end{description}
        \item[Challenge] When $\mathcal{A}$ submits challenge series
        \begin{equation*}
            \langle(i,t^*,x^{(t^*)(0)}_{i,1},\dots,x^{(t^*)(0)}_{i,m})\,|\,i \in S\rangle
        \end{equation*}
        and
        \begin{equation*}
            \langle(i,t^*,x^{(t^*)(1)}_{i,1},\dots,x^{(t^*)(1)}_{i,m})\,|\, i \in S\rangle\,,
        \end{equation*}
        choose weights $\omega^{(t^*)}_j,1 \leq j \leq m$ for instance $t^*$ and submit AO challenge series
        \begin{equation*}
            \langle(i,t^*,\sum^m_{j=1}x^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j)\,|\,i \in S\rangle
        \end{equation*}
        and
        \begin{equation*}
            \langle(i,t^*,\sum^m_{j=1}x^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j)\,|\,i \in S\rangle\,,
        \end{equation*}
        to $\mathcal{C}$. The received response if of the form 
        \begin{equation*}
            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}H(t^*)^{sk_i}\,|\,i\in U\rangle\,,
        \end{equation*}
        for an unknown $b \in \{0,1\}$. Multiply series elements by $r_i^N,\,1 \leq i \leq n$ for randomly chosen $r_i \in \mathbb{Z}_N$ and return
        \begin{equation*}
            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}r_i^N H(t^*)^{sk_i}\,|\,i\in U\rangle
        \end{equation*}
        to $\mathcal{A}$.
        \item[Guess] When $\mathcal{A}$ makes guess $b'$, make the same guess $b'$ to $\mathcal{C}$.
    \end{description}

@@

The combined quantisation and encoding function $\mathsf{E}_{r,f,m}(x)$ of a given a real number $x \in \mathbb{R}$, integer range $\mathbb{Z}_r$, and the desired scaling for $m$ prior encoded multiplications, is given by
\begin{equation}
    \mathsf{E}_{r,f,m}(x) = \left\lfloor f^{m+1} x \right\rceil \pmod{r}\,. \label{eqn:encode}
\end{equation}
Decoding of an integer $e \in \mathbb{Z}_r$, is given by
\begin{equation}
    \mathsf{E}^{-1}_{r,f,m}(e) \!=\! 
    \begin{dcases}
        \frac{e\hspace{-8pt}\pmod{r}}{f^{m+1}}, &e\hspace{-8pt}\pmod{r} \leq \left\lfloor\frac{r}{2}\right\rfloor \\
        -\frac{r - e\hspace{-8pt}\pmod{r}}{f^{m+1}}, &\text{otherwise} \\
    \end{dcases}.\label{eqn:decode}
\end{equation}

@@

\subsection{Extended Information Filter}
The Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982} is a reformulation of the Extended Kalman Filter (EKF), such that the update equations are simplified to sums of measurement information from each sensor. This requires the conversion of state estimate $\rvec{x}_k$ and estimate covariance $\mat{P}_k$ to the information vector and matrix
\begin{equation}
    \rvec{y}_k = \mat{P}_k^{-1}\rvec{x}_k \quad\textrm{and}\quad \mat{Y}_k = \mat{P}_k^{-1}\,,
\end{equation}
respectively. In this form, the update equations for $n$ measurements at time $k$, given process and measurement models \eqref{eqn:process_model} and \eqref{eqn:measurement_model}, are given by
\begin{equation}
    \rvec{y}_k = \rvec{y}_{k} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\rvec{x}_k) + \mat{H}_{k,i}\rvec{x}_k) \label{eqn:eif_info_vec_update}
\end{equation}
and
\begin{equation}
    \mat{Y}_k = \mat{Y}_{k} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
\end{equation}
with Jacobians
\begin{equation}
    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_k} \label{eqn:measurement_jacobian}
\end{equation}
for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\rvec{y}_k$ and matrix $\mat{Y}_k$ back to state estimate and covariance 
\begin{equation}
    \rvec{x}_k = \mat{Y}_k^{-1}\rvec{y}_k \quad\textrm{and}\quad \mat{P}_k = \mat{Y}_k^{-1}\,,
\end{equation}
before using the normal EKF prediction equations
\begin{equation}
    \rvec{x}_k = \vec{f}(\rvec{x}_{k-1})
\end{equation}
and
\begin{equation}
    \mat{P}_k = \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top\,,
\end{equation}
with Jacobian
\begin{equation}
    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\rvec{x}_{k-1}}\,. \label{eqn:jacobian_f}
\end{equation}

@@

\section{Privacy-Preserving Localisation} \label{sec:priv_localisation}
With the relevant preliminaries, we now apply the LCAO secure scheme to our original localisation problem. Recall we are considering a navigator in the presence of $n$ range sensors. The navigator runs a local filter, computing its update step with equations \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}, where received information from each sensor $i$ consists of the measurement vector
\begin{equation}
    \rvec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i (\rv{z}_{k,i} - h_i(\rvec{x}_k) + \mat{H}_{k,i}\rvec{x}_k) \label{eqn:measurement_vec}
\end{equation}
and the measurement matrix
\begin{equation}
    \mat{I}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:measurement_mat}
\end{equation}
at each time-step $k$. In this form, all sensitive sensor information is exclusively found in $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$. Namely, their measurements $\rv{z}_{k,i}$, measurement variances $r_i$ and locations $\vec{s}_i$; captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$.

The reason for using a linear-combination aggregation scheme in this scenario is due to computing $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ at the sensors requiring the navigator to disclose some location information in $\rvec{x}_k$, for the computing of Jacobians $\mat{H}_{k,i}$. Instead, we want to reformulate $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ such that the sensors can use the LCAO secure scheme, with location information in $\rvec{x}_k$ as weights from the navigator. As was shown in Section \ref{subsec:our_scheme}, this guarantees that sensors cannot learn navigator location information $\rvec{x}_k$, and that the navigator cannot learn individual sensor values required for computing $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$. From \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} we see that such a linear reformulation will set requirements on the possible measurement functions $h_i$.

@@

\subsection{Localisation Measurement Model} \label{subsec:observation_model}
Recalling the state definition \eqref{eqn:state_def} and two-dimensional measurement model \eqref{eqn:measurement_model}, we can see that $h_i$ \textit{cannot} be rearranged to a linear combination of elements private to the navigator. In addition, the Jacobian of $h_i$,
\begin{equation}
    \mat{H}_{k,i} = 
    \begin{bmatrix}
        \frac{\rv{x}_k - s_{x,i}}{\sqrt{(\rv{x}_k - s_{x,i})^2 + (\rv{y}_k - s_{y,i})^2}} \\
        \frac{\rv{y}_k - s_{y,i}}{\sqrt{(\rv{x}_k - s_{x,i})^2 + (\rv{y}_k - s_{y,i})^2}} 
    \end{bmatrix}\,,
\end{equation}
cannot be either. Instead, we consider the modified measurement functions
\begin{equation}
    h'_i(\rvec{x}_k) = h_i(\rvec{x}_k)^2\,. \label{eqn:modified_measurement_func}
\end{equation}
A measurement function in this form allows rearrangement to a linear combination of navigator information, and thus of the corresponding modified measurement vector $\rvec{i}'_{k,i}$ and measurement matrix $\mat{I}'_{k,i}$ as well. The modified measurement functions $h'_i$ can be written as
\begin{equation}
    \begin{split}
        h'_i(\rvec{x}_k) &= \left\lVert
        \begin{bmatrix}
            \rv{x}_k & \rv{y}_k
        \end{bmatrix}^\top - \vec{s}_i\right\rVert^2 \\
        &= (\rv{x}_k - s_{x,i})^2 + (\rv{y}_k - s_{y,i})^2 \\
        &= \rv{x}_k^2 + \rv{y}_k^2 -2s_{x,i}\rv{x}_k -2s_{y,i}\rv{y}_k +s_{x,i}^2 +s_{y,i}^2
    \end{split}\,,
\end{equation}
and the corresponding Jacobians $\mat{H}'_{k,i}$ as
\begin{equation}
    \mat{H}'_{k,i} = 
    \begin{bmatrix}
        2\rv{x}_k - 2s_{x,i} \\
        2\rv{y}_k - 2s_{y,i}
    \end{bmatrix}\,.
\end{equation}
The above have been rearranged as linear combinations of the weights $\rv{x}_k^2$, $\rv{y}_k^2$, $\rv{x}_k$ and $\rv{y}_k$, which capture all the required information that is private to the navigator.

@@

\begin{algorithm}[htbp]
    \caption{Navigator Prediction}\label{alg:nav_prediction}
    \begin{algorithmic}[1]
        \Procedure{Prediction}{$\rvec{x}_{k-1}$, $\mat{P}_{k-1}$, $\vec{f}$, $\mat{Q}$, $N$}

        \State Compute $\mat{F}_k$ by \eqref{eqn:jacobian_f}
        \State $\rvec{x}_{k} \gets \vec{f}(\rvec{x}_{k-1})$
        \State $\mat{P}_{k} \gets \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top + \mat{Q}$

        \For{$\rv{\omega}$ in $\langle\rv{x}_k^3,\rv{y}_k^3,\rv{x}_k^2\rv{y}_k,\rv{x}_k\rv{y}_k^2,\rv{x}_k^2,\rv{y}_k^2,\rv{x}_k\rv{y}_k,\rv{x}_k,\rv{y}_k\rangle$} 
            \State Compute $\mathsf{E}_{0}(\rv{\omega})$ by \eqref{eqn:encode}
            \State Compute $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{\omega}))$ by \eqref{eqn:our_scheme_encrypt}
            \State Broadcast $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{\omega}))$ to sensors
        \EndFor

        \State \Return $\rvec{x}_{k}, \mat{P}_{k}$
        \EndProcedure
    \end{algorithmic}
    \end{algorithm}

@@

    \While{Navigator broadcasting}
    \State Recieve $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_k))$
    \State Recieve remaining weights in the form above
    \EndWhile

>>>>

\subsection{Notation}
Throughout this work, we will use the following notation. Lowercase characters are scalars, $a$, vectors are underlined, $\vec{a}$, and random variables are bold, $\rv{a}$. Uppercase bold characters are matrices, $\mat{A}$, with $\mat{A}^{-1}$ denoting the inverse and $\mat{A}^\top$ the transpose. $|a|$ is the absolute value of $a$ and $\lVert\vec{a}\rVert$ the vector normal. Subscripts $\rv{x}_{k|j}$ will denote an estimate of $\rv{x}_k$ using measurements from times up to and including $j$. $\E{\cdot}$ and $\Var{\cdot}$ are used for the expected value and variance, respectively, and encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$. Additionally, key $k$ may be ommited when inferrable from context. $\lfloor\cdot\rceil$ rounds to the nearest integer, $a\|b$ stands for a bitwise concatenation of $a$ and $b$ and sets will be written as $\{\dots\}$ while ordered sequences as $\langle\dots\rangle$.

@@

The navigator state is defined as 
\begin{equation}
    \rvec{x} = 
    \begin{bmatrix}
        \rv{x} & \rv{dx} & \rv{y} & \rv{dy}
    \end{bmatrix}^\top\,. \label{eqn:state_def}
\end{equation}
A known process model is followed, which at time $k$ is given by
\begin{equation}
    \rvec{x}_k = \vec{f}(\rvec{x}_{k-1})+\rvec{w}_k\,, \label{eqn:process_model}
\end{equation}
with zero-mean Gaussian process noise $\rvec{w}_k \sim \mathcal{N}(\vec{0},\mat{Q})$. The measurement model is dependant on sensor $i$ and given by
\begin{equation}
    \rv{z}_{k,i} = h_i(\rvec{x}_k)+\rv{v}_{k,i}\,, \label{eqn:measurement_model}
\end{equation}
with noise $\rv{v}_{k,i} \sim \mathcal{N}(0,r_i)$, and measurement function $h_i$ for sensor $i$ at location
\begin{equation}
    \vec{s}_i = 
    \begin{bmatrix}
        s_{x,i} & s_{y,i}
    \end{bmatrix}^\top\,,
\end{equation} 
defined as
\begin{equation}
    \begin{split}
        h_i(\rvec{x}) &= \left\lVert
        \begin{bmatrix}
            \rv{x} & \rv{y}
        \end{bmatrix}^\top
        - \vec{s}_{i}\right\rVert \\
        &= \sqrt{(\rv{x}-s_{x,i})^2 + (\rv{y}-s_{y,i})^2}\,.
    \end{split}
\end{equation}
We wish to run a state estimation filter with models \eqref{eqn:process_model} and \eqref{eqn:measurement_model} such that all involved sensors $1 \leq i \leq n$ do not learn state estimates of $\rvec{x}_{k}$ and the navigator does not learn sensor locations $\vec{s}_i,\,1 \leq i \leq n$, measurement variances $r_i$ or their measurements $\rv{z}_{k,i}$ at any time $k$. We motivate these goals with the example of aircraft navigation in the presence of privately-operated range-measuring stations. It is reasonable to assume that the current state of an aircraft may not wish to be disclosed to unknown parties and, similarly, that tower locations may wish to be kept private from unidentified navigating aircraft. However, the additional safety to passengers provided by accurate aircraft localisation, may be a goal of all those involved justifying their cooperation.

@@

\begin{pf}
    Consider adversary $\mathcal{A}$ playing the LCAO game defined in Section \ref{subsec:lcao}. The following is a construction of an adversary $\mathcal{A}'$ playing the AO game in Appendix \ref{app:ao} against a challenger $\mathcal{C}$ using the Joye-Libert aggregation scheme from Section \ref{subsec:joye_libert_scheme}.
    \begin{description}
        \item[Setup] When receiving $N$ and $H$ as public parameters from $\mathcal{C}$, choose an $m>1$ and give public parameter $H$, number of weights $m$, and $pk_0=N$ to $\mathcal{A}$.
        \item[Queries] Handle queries from $\mathcal{A}$:
        \begin{description}
            \item[\textit{Weight Query}] When $\mathcal{A}$ submits a weight query $t$, choose weights $\omega^{(t)}_j,\,1 \leq j \leq m$ and random values $r_j \in \mathbb{Z}_N,\,1 \leq j \leq m$, and return encryptions 
            \begin{equation*}
                (N+1)^{\omega^{(t)}_{j}}r_j^N\pmod{N^2},\,1\leq j\leq m
            \end{equation*}
            to $\mathcal{A}$.
            \item[\textit{Combine Query}] When $\mathcal{A}$ submits combine query $(i, t, x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$, choose weights $\omega^{(t)}_j,1 \leq j \leq m$ if not already chosen for the instance $t$, and make an AO encryption query $(i, t, \sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ to $\mathcal{C}$. The received response will be of the form $(N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}H(t)^{sk_i}$; multiply it by $r^N$ for a random $r \in \mathbb{Z}_N$ and return 
            \begin{equation*}
                (N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r^N H(t)^{sk_i} \pmod{N^2}
            \end{equation*}
            to $\mathcal{A}$.
            \item[\textit{Compromise Query}] When $\mathcal{A}$ submits compromise query $i$, make the same compromise query $i$ to $\mathcal{C}$, and return the recieved secret key $sk_i$ to $\mathcal{A}$.
        \end{description}
        \item[Challenge] When $\mathcal{A}$ submits challenge series
        \begin{equation*}
            \langle(i,t^*,x^{(t^*)(0)}_{i,1},\dots,x^{(t^*)(0)}_{i,m})\,|\,i \in S\rangle
        \end{equation*}
        and
        \begin{equation*}
            \langle(i,t^*,x^{(t^*)(1)}_{i,1},\dots,x^{(t^*)(1)}_{i,m})\,|\, i \in S\rangle\,,
        \end{equation*}
        choose weights $\omega^{(t^*)}_j,1 \leq j \leq m$ for instance $t^*$ and submit AO challenge series
        \begin{equation*}
            \langle(i,t^*,\sum^m_{j=1}x^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j)\,|\,i \in S\rangle
        \end{equation*}
        and
        \begin{equation*}
            \langle(i,t^*,\sum^m_{j=1}x^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j)\,|\,i \in S\rangle\,,
        \end{equation*}
        to $\mathcal{C}$. The received response will be of the form 
        \begin{equation*}
            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}H(t^*)^{sk_i}\,|\,i\in U\rangle\,,
        \end{equation*}
        for an unknown $b \in \{0,1\}$. Multiply series elements by $r_i^N,\,1 \leq i \leq n$ for randomly chosen $r_i \in \mathbb{Z}_N$ and return
        \begin{equation*}
            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}r_i^N H(t^*)^{sk_i}\,|\,i\in U\rangle
        \end{equation*}
        to $\mathcal{A}$.
        \item[Guess] When $\mathcal{A}$ makes guess $b'$, make the same guess $b'$ to $\mathcal{C}$.
    \end{description}

@@

The function for combined quantisation and encoding $\mathsf{E}_{r,f,m}(x)$, of a given a real number $x \in \mathbb{R}$, integer range $\mathbb{Z}_r$, and the desired scaling for $m$ prior encoded multiplications, is given by
\begin{equation}
    \mathsf{E}_{r,f,m}(x) = \left\lfloor f^{m+1} x \right\rceil \pmod{r}\,. \label{eqn:encode}
\end{equation}
Decoding of an integer $e \in \mathbb{Z}_r$, is given by
\begin{equation}
    \mathsf{E}^{-1}_{r,f,m}(e) \!=\! 
    \begin{dcases}
        \frac{e\hspace{-8pt}\pmod{r}}{f^{m+1}}, &e\hspace{-8pt}\pmod{r} \leq \left\lfloor\frac{r}{2}\right\rfloor \\
        -\frac{r - e\hspace{-8pt}\pmod{r}}{f^{m+1}}, &\text{otherwise} \\
    \end{dcases}.\label{eqn:decode}
\end{equation}

@@

\subsection{Extended Information Filter}
The Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982} is a reformulation of the Extended Kalman Filter (EKF), such that the update equations are simplified to sums of measurement information from each sensor. This requires the conversion of predicted state estimate $\rvec{x}_{k|k-1}$ and estimate covariance $\mat{P}_{k|k-1}$ to the information vector and matrix
\begin{equation}
    \rvec{y}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\rvec{x}_{k|k-1} \quad\textrm{and}\quad \mat{Y}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\,,
\end{equation}
respectively. In this form, the update equations for $n$ measurements at time $k$, given process and measurement models \eqref{eqn:process_model} and \eqref{eqn:measurement_model}, are given by
\begin{equation}
    \begin{split}
        &\rvec{y}_{k|k} = \rvec{y}_{k|k-1} + \\
        &\quad \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\rvec{x}_{k|k-1}) + \mat{H}_{k,i}\rvec{x}_{k|k-1})
    \end{split} \label{eqn:eif_info_vec_update}
\end{equation}
and
\begin{equation}
    \mat{Y}_{k|k} = \mat{Y}_{k|k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
\end{equation}
with Jacobians
\begin{equation}
    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_{k|k-1}} \label{eqn:measurement_jacobian}
\end{equation}
for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\rvec{y}_{k|k}$ and matrix $\mat{Y}_{k|k}$ back to state estimate and covariance 
\begin{equation}
    \rvec{x}_{k|k} = \mat{Y}_{k|k}^{-1}\rvec{y}_{k|k} \quad\textrm{and}\quad \mat{P}_{k|k} = \mat{Y}_{k|k}^{-1}\,,
\end{equation}
before using the normal EKF prediction equations
\begin{equation}
    \rvec{x}_{k+1|k} = \vec{f}(\rvec{x}_{k|k})
\end{equation}
and
\begin{equation}
    \mat{P}_{k+1|k} = \mat{F}_k\mat{P}_{k|k}\mat{F}_k^\top\,,
\end{equation}
with Jacobian
\begin{equation}
    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\rvec{x}_{k|k}}\,. \label{eqn:jacobian_f}
\end{equation}

@@

\section{Privacy-Preserving Localisation} \label{sec:priv_localisation}
With the relevant preliminaries, we now apply the LCAO secure scheme to our original localisation problem. Recall we are considering a navigator in the presence of $n$ range sensors. The navigator runs a local filter, computing its update step with equations \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}, where received information from each sensor $i$ consists of the measurement vector
\begin{equation}
    \rvec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i (\rv{z}_{k,i} - h_i(\rvec{x}_{k|k-1}) + \mat{H}_{k,i}\rvec{x}_{k|k-1}) \label{eqn:measurement_vec}
\end{equation}
and the measurement matrix
\begin{equation}
    \mat{I}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:measurement_mat}
\end{equation}
at each time-step $k$. In this form, all sensitive sensor information is exclusively found in $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$. Namely, their measurements $\rv{z}_{k,i}$, measurement variances $r_i$ and locations $\vec{s}_i$; captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$.

The reason for using a linear-combination aggregation scheme in this scenario is due to computing $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ at the sensors requiring the navigator to disclose some location information in $\rvec{x}_{k|k-1}$, for the computing of Jacobians $\mat{H}_{k,i}$. Instead, we want to reformulate $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ such that the sensors can use the LCAO secure scheme, with location information in $\rvec{x}_{k|k-1}$ as weights from the navigator. As was shown in Section \ref{subsec:our_scheme}, this guarantees that sensors cannot learn navigator location information $\rvec{x}_{k|k-1}$, and that the navigator cannot learn individual sensor values required for computing $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$. From \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} we see that such a linear reformulation will set requirements on the possible measurement functions $h_i$.

@@

\subsection{Localisation Measurement Model} \label{subsec:observation_model}
Recalling the state definition \eqref{eqn:state_def} and two-dimensional measurement model \eqref{eqn:measurement_model}, we can see that $h_i$ \textit{cannot} be rearranged to a linear combination of elements private to the navigator. In addition, the Jacobian of $h_i$ at $\rvec{x}_{k|k-1}$,
\begin{equation}
    \mat{H}_{k,i} = 
    \begin{bmatrix}
        \frac{\rv{x}_{k|k-1} - s_{x,i}}{\sqrt{(\rv{x}_{k|k-1} - s_{x,i})^2 + (\rv{y}_{k|k-1} - s_{y,i})^2}} \\
        \frac{\rv{y}_{k|k-1} - s_{y,i}}{\sqrt{(\rv{x}_{k|k-1} - s_{x,i})^2 + (\rv{y}_{k|k-1} - s_{y,i})^2}} 
    \end{bmatrix}\,,
\end{equation}
cannot be either. Instead, we consider the modified measurement functions
\begin{equation}
    h'_i(\rvec{x}) = h_i(\rvec{x})^2\,. \label{eqn:modified_measurement_func}
\end{equation}
A measurement function in this form allows rearrangement to a linear combination of navigator information, and thus of the corresponding modified measurement vector $\rvec{i}'_{k,i}$ and measurement matrix $\mat{I}'_{k,i}$ as well. The modified measurement functions $h'_i$ can be written as
\begin{equation}
    \begin{split}
        h'_i(\rvec{x}) &= \left\lVert
        \begin{bmatrix}
            \rv{x} & \rv{y}
        \end{bmatrix}^\top - \vec{s}_i\right\rVert^2 \\
        &= (\rv{x} - s_{x,i})^2 + (\rv{y} - s_{y,i})^2 \\
        &= \rv{x}^2 + \rv{y}^2 -2s_{x,i}\rv{x} -2s_{y,i}\rv{y} +s_{x,i}^2 +s_{y,i}^2
    \end{split}\,,
\end{equation}
and the corresponding Jacobians $\mat{H}'_{k,i}$ as
\begin{equation}
    \mat{H}'_{k,i} = 
    \begin{bmatrix}
        2\rv{x}_{k|k-1} - 2s_{x,i} \\
        2\rv{y}_{k|k-1} - 2s_{y,i}
    \end{bmatrix}\,. \label{eqn:modified_jacobian}
\end{equation}
From the above we see that $h'_i(\rvec{x}_{k|k-1})$ and $\mat{H}'_{k,i}$ can be rearranged as linear combinations of the weights $\rv{x}_{k|k-1}^2$, $\rv{y}_{k|k-1}^2$, $\rv{x}_{k|k-1}$ and $\rv{y}_{k|k-1}$, which capture all the required information that is private to the navigator.

@@

\begin{algorithm}[htbp]
    \caption{Navigator Prediction}\label{alg:nav_prediction}
    \begin{algorithmic}[1]
        \Procedure{Prediction}{$\rvec{x}_{k-1|k-1}$, $\mat{P}_{k-1|k-1}$, $\vec{f}$, $\mat{Q}$, $N$}

        \State Compute $\mat{F}_k$ by \eqref{eqn:jacobian_f}
        \State $\rvec{x}_{k|k-1} \gets \vec{f}(\rvec{x}_{k-1|k-1})$
        \State $\mat{P}_{k|k-1} \gets \mat{F}_k\mat{P}_{k-1|k-1}\mat{F}_k^\top + \mat{Q}$

        \For{$\rv{\omega}$ in \eqref{eqn:weights_to_broadcast}} 
            \State Compute $\mathsf{E}_{0}(\rv{\omega})$ by \eqref{eqn:encode}
            \State Compute $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{\omega}))$ by \eqref{eqn:our_scheme_encrypt}
            \State Broadcast $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{\omega}))$ to sensors
        \EndFor

        \State \Return $\rvec{x}_{k|k-1}, \mat{P}_{k|k-1}$
        \EndProcedure
    \end{algorithmic}
    \end{algorithm}

@@

    \While{Navigator broadcasting}
    \State Recieve $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_{k|k-1}))$
    \State Recieve remaining weights in the form above
    \EndWhile
